---
title: "Irisdataset"
author: "sachin reddy"
date: "13/12/2021"
output:
  html_document: default
  pdf_document: default
---

statistical analysis of iris dataset

```{r}
library(datasets)
data<-data.frame(iris)
str(data)
```


summary of iris dataset

```{r}
summary(data)

```
mean of sepal length and petal length respectively
```{r}
mean(data$Sepal.Length)

mean(data$Petal.Length)

```
median of sepal width and petal width  respectively

```{r}
median(data$Sepal.Width)

median(data$Petal.Width)

```
#range of sepal length

```{r}
range<-function(n){
  range1=max(n)-min(n)
  return(range1)
}
range(data$Sepal.Length)

```
dispersion measures
#quantiles and inter quantile of sepals

```{r}
quantile(data$Sepal.Length)

quantile(data$Sepal.Width)

IQR(data$Sepal.Length)

IQR(data$Sepal.Width)

```
variance and standard deviation
```{r }
var(data$Sepal.Length)
sd(data$Sepal.Width)
var(data$Petal.Length)

```
table  and sort of sepal width
```{r }
tab<-table(data$Sepal.Width)
tab

sort(tab,decreasing=TRUE)


```

## Including Plots

#boxplotting

```{r }
boxplot(data,main='species')

```

#barplot of sepal length
```{r }
barplot(head(data$Sepal.Length))

```






#creating histogram of sepal width
```{r }
hist(data$Sepal.Width,main='species',xlab = 'species width')


```

#plotting of iris data

```{r}
plot(data$Petal.Length,data$Petal.Width,main='plotting of iris data')
```
